\documentclass[10pt,-letter paper]{article}
\usepackage[left=1in, right=0.75in, top=1in, bottom=0.75in]{geometry}
\usepackage{graphicx} % Required for inserting images
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
\doublespacing
\singlespacing
\usepackage[none]{hyphenat}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{amsthm}
\interdisplaylinepenalty=2500
%\savesymbol{iint}
\usepackage{txfonts}
%\restoresymbol{TXF}{iint}
\usepackage{wasysym}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{txfonts}
\let\vec\mathbf{}
\usepackage{stfloats}
\usepackage{float}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
\usepackage{amssymb}
%\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{eenrc}
%\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
%\usepackage{listings}
\usepackage[latin1]{inputenc}
%%\usepackage{color}{   
%%\usepackage{lscape}
\usepackage{textcomp}
\usepackage{titling}
\usepackage{hyperref}
%\usepackage{fulbigskip}   
\usepackage{tikz}
\usepackage{graphicx}
\lstset{
  frame=single,
  breaklines=true
}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{siunitx}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tfrupee}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mwe} % for blindtext and example-image-a in example
\usepackage{wrapfig}
\graphicspath{{figs/}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\newcommand{\sgn}{\mathop{\mathrm{sgn}}}
\providecommand{\abs}[1]{\left\vert#1\right\vert}
\providecommand{\res}[1]{\Res\displaylimits_{#1}} 
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
%\providecommand{\norm}[1]{\lVert#1\rVert}
\providecommand{\mtx}[1]{\mathbf{#1}}
\providecommand{\mean}[1]{E\left[ #1 \right]}
\providecommand{\fourier}{\overset{\mathcal{F}}{ \rightleftharpoons}}
%\providecommand{\hilbert}{\overset{\mathcal{H}}{ \rightleftharpoons}}
\providecommand{\system}{\overset{\mathcal{H}}{ \longleftrightarrow}}
	%\newcommand{\solution}[2]{\textbf{Solution:}{#1}}
%\newcommand{\solution}{\noindent \textbf{Solution: }}
\newcommand{\cosec}{\,\text{cosec}\,}
\providecommand{\dec}[2]{\ensuremath{\overset{#1}{\underset{#2}{\gtrless}}}}
\newcommand{\myvec}[1]{\ensuremath{\begin{pmatrix}#1\end{pmatrix}}}
\newcommand{\myaugvec}[2]{\ensuremath{\begin{amatrix}{#1}#2\end{amatrix}}}
\newcommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\title{MATHEMATICS}
\date{\today}
\begin{document}

\maketitle

\begin{enumerate}
\section{Matrices}
\item In the interval ${\pi}/2<x<\pi$, find the value of $x$ for which the matrix $\myvec{2\sin{x} & 3 \\ 1 & 2\sin{x}}$ is singular.\\
\item Express the matrix $A = \myvec{2&4&-6\\7&3&5\\1&-2&4}$ as the sum of a symmetric and skew symmetric matrix. \\
\item A trust fund has \rupee $35,000$ is to be invested in two different types of bonds. The first bond pays $8\%$ interest per annum which will be given to orphanage and second bond pays $10\%$ interest per annum which will be given to an N.G.O. (Cancer Aid Society). Using matrix multiplication, determine how to divide \rupee $35,000$ among two types of bonds if the trust fund obtains an annual total interest of \rupee $3,200$. What are the values reflected in this question? \\
\item If $A = \myvec{2&3\\1&-4}, B = \myvec{1&-2\\-1&3}$, verify that $(AB)^{-1} = B^{-1}A^{-1}$. \\
\item Using properties of determinant, solve for $x$:
$\mydet{a+x & a-x & a-x \\ a-x & a+x & a-x \\ a-x & a-x & a+x} = 0$ \\
\section{probability}
\item Four cards are drawn successively with replacement from a well shuffled deck of $52$ cards. What is the probability that
\begin{enumerate}
\item all the four cards are spades?
\item only $2$ cards are spades?
\end{enumerate}
\item A pair of dice is thrown $4$ times, If getting a doublet is considered a success, find the probabbility distribution of number of successes. Hence find the mean of the distribution. \\
\item In answering a question on a multiple choice test, a student either knows the answer or guesses. Let $\frac{3}{5}$ be the probability that he knows the answer and $\frac{2}{5}$ be the probability that he guesses. Assuming that a student who gusses at the answer will be correct with probability $\frac{1}{3}$, what is the probability that the student knows the answer given that he answered it correctly?\\
\section{Algebra}
\item Prove that $2\tan^{-1}\brak{\frac{1}{2}}+\tan^{-1}\brak{\frac{1}{7}} = \sin^{-1}\brak{\frac{31}{25\sqrt{2}}}$. \\
\item Solve for x: $\tan^{-1}\brak{\frac{1-x}{1+x}} = \frac{1}{2}\tan^{-1}x$, $x>0$. \\
\section{vector}
\item Write the direction ratios of the vector $3\vec{a}+2\vec{b}$ where $\vec{a} = \vec{i}+\vec{j}-2\vec{k}$ and $\vec{b} = 2\vec{i}-4\vec{j}+5\vec{k}$. \\
\item Find the projection of the vector $\vec{a}=2\vec{i}+3\vec{j}+2\vec{k}$ on the vector $\vec{b}=2\vec{i}+2\vec{j}+\vec{k}$. \\
\item Write the vector equation of the line passing through $\brak{1,2,3}$ and perpendicular to the plane $\vec{r}\cdot\brak{\vec{i}+2\vec{j}-5\vec{k}}+9=0$. \\
\item Prove that $[\vec{a},\vec{b}+\vec{c},\vec{d}] = [\vec{a},\vec{b},\vec{d}]+[\vec{a},\vec{c},\vec{d}]$.  \\
\item Find the shortrest distance between the following lines:\\
$\vec{r} = 2\vec{i}-5\vec{j}+\vec{k} +\lambda\brak{3\vec{i}+2\vec{j}+6\vec{k}}$ and $\vec{r} = 7\vec{i}-6\vec{k}+\mu\brak{\vec{i}+2\vec{j}+2\vec{k}}$. \\
\item Find the vector and cartesian equations of the plane passing through the line of intersection of planes \\
$\vec{r}\cdot\brak{2\vec{i}+2\vec{j}-3\vec{k}}=7$, \quad $\vec{r}\cdot\brak{2\vec{i}+5\vec{j}+3\vec{k}}=9$\\
such that the intercepts made by the plane on x-axis and z-axis are equal.\\
\section{Differentiation}
\item For what value of $\lambda$ the function defined by $f(x) = \begin{cases} \lambda\brak{x^2+2}&, if x \leq 0 \\ 4x+6&, if x>0 \end{cases}$is continuous at $x=0$? Hence check the differentiability of $f(x)$ at $x=0$. \\
\item If $x = ae^t\brak{\sin{t}+\cos{t}}$ and $y = ae^t\brak{\sin{t}-\cos{t}}$, prove that $\frac{dy}{dx}=\frac{x+y}{x-y}$. \\
\item if $y = Ae^{mx} + Be^{nx}$, show that $\frac{d^{2}y}{dx^2} -\brak{m+n}\frac{dy}{dx} + mny = 0$. \\
\item The sum of surface areas of a spere and a cuboid with sides $\frac{x}{3}$, $x$ and $2x$ is constant . Show that the sum of their volumes is minimum if $x$ is equal to three times the radius of sphere.\\
\section{Integration}
\item Find the solution to the differential equation 
$\frac{dy}{dx} = x^{3}e^{-2y}$
\item Write the integrating factor of the differential equation
$\sqrt{x}\frac{dy}{dx} + y = e^{-2\sqrt{x}}$ \\
\item Find $\int \frac{x}{\brak{x^2+1}\brak{x-1}}dx$.\\
\item Find $\int_{0}^{\frac{1}{\sqrt{2}}} \frac{\sin^{-1}x}{{\brak{1-x^2}}^{3/2}}dx$.\\
\item Find $\int \frac{x+3}{\sqrt{5-4x-2x^2}}dx$.\\
\item Solve the differential equation: \\
$\brak{x\sin^2{\brak{\frac{y}{x}}}-y}dx +xdy = 0$ given $y = \frac{\pi}{4}$ when $x=1$.\\
\item Solve the differential equation $\frac{dy}{dx}-3y\cot{x} = \sin{2x}$ given $y=2$ when $x=\frac{\pi}{2}$.\\
\section{Linear forms}
\item Find the area of the region $\cbrak{\brak{x,y} : y^2 \leq 4x, 4x^2+4y^2 \leq 9}$, using integration.\\
\item Using integration, find the area enclosed by the parabola $4y = 3x^2$ and the line $2y = 3x+12$. \\
\section{Functions}
\item Show that the relation $R$ in the set $A = \{1,2,3,4,5\}$ given by $R = \{\brak{a,b} : |a-b| \text{ is divisible by 2}\}$ is an equivalence relation. Write all the equivalence classes of $R$. \\ 
\section{Optimization}
\item A manufacturer produces nuts and bolts. It takes $2$ hours work on machine $A$ and $3$ hours work on machine $B$ to produce a package of nuts. It takes $3$ hours on machine $A$ and $2$ hours on machine $B$ to produce a package of bolts. He earns a profit of \rupee $24$ per package on nuts and \rupee 18 per package on bolts. How many packages of each should be produced each day so as to maximize his profit, if he operates his machines for at the most $10$ hours a day. Make an L.P.P. from above and solve it graphically.
\end{enumerate}
\end{document}\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{CBSE Paper}
\author{Aryan Jain}
\date{February 2024}

\begin{document}

\maketitle

\section{Introduction}

\end{document}
